method

### 2022-02-22 06_Paper/ER-ED/method.Rmd
fixed issue with heading
deleted old packages

library(readxl)     # import excel files
library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CERED.txt")

library(papaja)     # APA conform output
#library(afex)       # for ANOVA
#library(emmeans)
#library(ggplot2)    # for nice plots
#library(dplyr)
#library(BayesFactor)
#library(effectsize)

```

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
```

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages ... <!-- name and reference the main analysis packages, agian for consistentcy with Zerna et al. --> for all our analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
<!-- Attention! OSF is still private --> 
## 2.1 Ethics information

>>>>

library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CERED.txt")

library(papaja)     # APA conform output
library(readxl)     # import excel files
```

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))

stim_neutral <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
```

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages ... <!-- name and reference the main analysis packages, agian for consistentcy with Zerna et al. --> for all our analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
<!-- Attention! OSF is still private -->

## 2.1 Ethics information
